---
output: github_document
---

```{r, include = FALSE, cache = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%",
  cache = FALSE,
  asciicast_theme = "pkgdown"
)

asciicast::init_knitr_engine(
  startup = quote({
    library(sunsets)
    set.seed(1) }),
  echo = TRUE,
  echo_input = FALSE
)

library(palettes)
```

# guzioR

A compilation of various commands and tools I've used that may be helpful. This package will not be routinely updated or maintained, but I'll add things as they come up.

## Installation

Install the development version from [GitHub](github.com) using the following:

```         
remotes::install_github("guziordo/guzioR")
```

## Usage

```
library(guzioR)
```

## Included Functions

<b>quick.boxplot</b> <br>
Just as is sounds, it's a quick and easy way to generate a box plot with points and statistics (if wanted).

## Included Palettes

These are compilations of palettes provided by friends or otherwise generated for fun.

```{r echo = F}
plot(guzioR::guzior.pal)
```
<i>Thank you Lydia-Ann Ghuneim, Ph.D. for providing the CPCOLS palette.</i>

### Big 10 Palettes
I don't own any of the rights to things from the Big 10. These are some palettes generated based on their brand identities. First two colors in each are the primary colors of that school.

```{r echo = F}
plot(guzioR::b10.pal)
```


